\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-05-20 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated some references in the manual, and fixed a statement that was not fully correct in the PDF file of the time scheme we use

For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.
A detailed theoretical analysis of the dispersion
and stability properties of the SEM is available in \citet{Coh02}, \citet{DeSe07} and \citet{SeOl07}.\\

>>>>

For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.
A detailed theoretical analysis of the dispersion
and stability properties of the SEM is available in \citet{Coh02}, \citet{DeSe07}, \citet{SeOl07} and \citet{SeOl08}.\\
